% LaTeX file for a 1 page document
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{fullpage}
\usepackage{url}
\usepackage{listings}

\lstdefinestyle{basic}{showstringspaces=false,columns=fullflexible,language=Python,
escapechar=@,xleftmargin=1pc,%
%basicstyle=\small\bfseries\itshape,%
%keywordstyle=\underbar,
mathescape=true,%
lineskip=-1pt,%
keepspaces=true,%
%basicstyle=\small\sffamily,%
basicstyle=\footnotesize\ttfamily,%
commentstyle=\mdseries\rmfamily,%
morekeywords={class,object,with,fun,new,end,int,bool,string},%
deletekeywords={error,apply,values,and,equal,eq},%
moredelim=**[is][\color{red}]{`}{`}
}
\lstset{style=basic}

\title{C343 Project 5 - Hash Tables in Compression}
\date{Due 11:59pm, November 11, 2016}

\begin{document}
\maketitle

\section{Assignment Description}

This week we return to our string compression program, but using our own
implementation of a hash table.


\section{Your Task}

We have given you a complete solution for Project 4, except that we have
replaced the uses of Java HashMaps with uses of the HashTableImp class,
defined in \lstinline{HashTableImp.java}. That class has stubs for all
methods that you need to implement:
\begin{enumerate}
\item \lstinline{V get(K key)} - return the value associated with the \lstinline{key}.
\item \lstinline{V put(K key, V value)} - associates the \lstinline{value} with the \lstinline{key} within the hashtable.
\item \lstinline{V remove(K key)} - remove the key-value item as specified by \lstinline{key}.
\item \lstinline{Set<K> keySet()} - return a set containing all the keys
  in the hashtable.
\item \lstinline{boolean containsKey(K key)} - returns true if the
  hashtable contains a mapping for the specified key.
\item \lstinline{boolean isEmpty()} - returns true if the hashtable contains no key-value mappings.
\end{enumerate}

We recommend that you implement hashtables using the chaining method
of collision avoidance and table doubling to control the load factor
and space consumption of the hash table.

\section{Running Your Code}
The same instructions for the DNA compression project.

\section{Deliverables}

Your repo folder should contain all the files from the zip.  These are
the ones you need to modify:
\begin{itemize}
\item \lstinline{HashTableImp.java} - containing your hash table implementation and unit tests
\end{itemize}

\section{Testing}
The same instructions for the DNA compression project.

\end{document}
